A fast algorithm for global code motion of congruent instructions

### 2017-11-11 cgo/paper.tex
acmart.cls

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

@@

\section{Introduction}

\label{sec:intro}
Compiler techniques to remove redundant computations are composed of an analysis
phase that detects identical computations in the program and a transformation
phase that reduces the number of run-time computations.  Classical scalar
optimizations like Common Subexpression Elimination (CSE) \cite{dragonbook} work
very well on single basic-blocks (local level) but when it comes to detect
redundancies across basic-blocks (global level) these techniques fall short:
more complex passes like Global Common Subexpression Elimination (GCSE) and
Partial Redundancy Elimination (\PRE{}) have been designed to handle these cases
based on data-flow analysis \cite{morel1979global}.  At first these techniques
were described in the classical data-flow analysis framework, but later the use
of Static Single Assignment (\SSA{}) representation lowered their cost in terms
of compilation time \cite{briggs1994effective,chow1997new,kennedy1999partial}
and brought these techniques in the main stream: \SSA{} based \PRE{} is
available in many compilers like \GCC{} and \LLVM{}.

>>>>

@@

\section{Introduction}
\label{sec:intro}
Compiler techniques to remove redundant computations are composed of an analysis
phase that detects identical computations in the program and a transformation
phase that reduces the number of run-time computations.  Classical scalar
optimizations like Common Subexpression Elimination (CSE) \cite{dragonbook} work
very well on single basic-blocks (local level) but when it comes to detect
redundancies across basic-blocks (global level) these techniques fall short:
more complex passes like Global Common Subexpression Elimination (GCSE) and
Partial Redundancy Elimination (\PRE{}) have been designed to handle these cases
based on data-flow analysis \cite{morel1979global}.  At first these techniques
were described in the classical data-flow analysis framework, but later the use
of Static Single Assignment (\SSA{}) representation lowered their cost in terms
of compilation time \cite{briggs1994effective,chow1997new,kennedy1999partial}
and brought these techniques in the main stream: \SSA{} based \PRE{} is
available in many compilers like \GCC{} and \LLVM{}.
